---
title: "O365 Surveys"
output:
  rmdformats::readthedown:
    highlight: pygments
---

<style type="text/css">
p{ /* Normal  */
   font-size: 12px;
}
body{ /* Normal  */
   font-size: 12px;
}
td {  /* Table  */
   font-size: 10px;
}
h1 { /* Header 1 */
 font-size: 26px;
 color: #4294ce;
}
h2 { /* Header 2 */
 font-size: 22px;
}
h3 { /* Header 3 */
 font-size: 18px;
}
code.r{ /* Code block */
  font-size: 10px;
}
pre { /* Code block */
  font-size: 10px
}
#table-of-contents h2 {
background-color: #4294ce;
}
#table-of-contents{
background: #688FAD;
}
#nav-top span.glyphicon{
color: #4294ce;
}
#postamble{
background: #4294ce;
border-top: ;
}
</style>


```{r echo=FALSE, message=FALSE, warning=FALSE}
if(!require(easypackages)){install.packages("easypackages")}
library(easypackages)
packages("plyr", "dplyr", "ggplot2", "tidyr", "stringr", "lubridate", "ggpubr", "gridExtra", "readxl", "scales", "modes", prompt = FALSE)

options(scipen = 999)#Avoid exponents in plots
```

https://gist.github.com/mrdwab/984707
http://hamelg.blogspot.com/2015/08/introduction-to-r-part-23-point.html


As with the confidence interval for the mean, you can use a built in R function to get a confidence interval for a population proportion instead of calculating it by hand. In this case, we use the prop.test() function:

```{r}
prop.test(x=204,      # Number of observations
          n=1000)     # Total number of samples

prop.test(x=204, n=1000, conf.level = .99)
```

The following code snippet allows you to substitute values and obtain a confidence interval based on the central limit theorem.

```{r}
# Code snippet to construct a confidence interval
  xbar = 100  # Sample Mean
  sd   = 10   # Population Standard Deviation
  n    = 25   # Sample size
  CL   = .95  # Required Confidence Level
  
  zstar <- qnorm(CL+.5*(1-CL)) # Obtain Z-score for this confidence level
  sd.xbar <- sd/sqrt(n)        # Compute standard of sample mean 
  ME <- zstar * sd.xbar        # Compute margin of error
  
  lb <- xbar - ME              # Compute lower bound of CI
  ub <- xbar + ME              # Compute upper bound of CI
  
  CI <- c(CL,lb,xbar,ub,ME)    # Put our results in a vector

  names(CI) <- c("Confidence Level","Lower Bound","Xbar","Upper Bound",
                 "Margin of Error") # Name the vector elements
  CI                           # Display the vector
```

suppose we had a sample mean of 123 based on a sample of size 50 and we knew that the sample was drawn from a population with a standard deviation of 15. What is a 95% confidence interval for the population mean.

```{r}
# Code snippet to construct a confidence interval
  xbar = 100  # Sample Mean
  sd   = 10   # Population Standard Deviation
  n    = 25   # Sample size
  CL   = .95  # Required Confidence Level
  
  zstar <- qnorm(CL+.5*(1-CL)) # Obtain Z-score for this confidence level
  sd.xbar <- sd/sqrt(n)        # Compute standard of sample mean 
  ME <- zstar * sd.xbar        # Compute margin of error
  
  lb <- xbar - ME              # Compute lower bound of CI
  ub <- xbar + ME              # Compute upper bound of CI
  
  CI <- c(CL,lb,xbar,ub,ME)    # Put our results in a vector

  names(CI) <- c("Confidence Level","Lower Bound","Xbar","Upper Bound",
                 "Margin of Error") # Name the vector elements
  CI                           # Display the vector
```

We can do the same kind of thing for confidence intervals for proportions.

The Sampling Distribution of the Proportion

We have the basic theoretical results.

The estimates of a proportion p^p^ based on a sample of size n is approsimately normal and has the following mean and standard deviation provided that np^>10np^>10 and n(1−p^)>10n(1−p^)>10.

μp^=p
μp^=p
and
σp^=p(1−p)n−−−−−−−√
σp^=p(1−p)n

Here is a code snippet. You can replace the values in the first few lines and run the entire snippet.

```{r}
# Code snippet to compute a confidence interval for a proportion

phat <- .7   # Estimated proportion
CL <- .95    # Required confidence level
n <- 100     # Sample size

zstar <- qnorm(CL+.5*(1-CL))
se.phat <-sqrt(phat*(1-phat)/n)

lb <- phat - zstar * se.phat
ub <- phat + zstar * se.phat

CI <- c(CL,lb,phat,ub)
names(CI) <- c("Confidence Level", "lower Bound","phat","Upper Bound")

CI
```

suppose we had a sample proportion of .2, a sample size of 1,000 and we wanted an 80% confidence interval for the population proportion.

```{r}
# Code snippet to compute a confidence interval for a proportion

phat <- .2    # Estimated proportion
CL <- .8      # Required confidence level
n <- 1000     # Sample size

zstar <- qnorm(CL+.5*(1-CL))
se.phat <-sqrt(phat*(1-phat)/n)

lb <- phat - zstar * se.phat
ub <- phat + zstar * se.phat

CI <- c(CL,lb,phat,ub)
names(CI) <- c("Confidence Level", "lower Bound","phat","Upper Bound")

CI
```


$$ p \pm z \sqrt{ \frac{p(1-p)}{n} } $$


To review

https://www.google.com/search?q=r+survey+results+analysis&ei=oP9gWvPsIYXejwO517vwDA&start=10&sa=N&biw=953&bih=1237

http://faculty.nps.edu/rdfricke/OA4109/Lab%207%20--%20Intro%20to%20R%20Survey%20Package.pdf
https://stats.idre.ucla.edu/r/faq/how-do-i-analyze-survey-data-with-a-simple-random-sample-design/
https://rpubs.com/corey_sparks/53683
http://r-survey.r-forge.r-project.org/survey/
https://cran.r-project.org/web/packages/survey/vignettes/survey.pdf
https://stats.idre.ucla.edu/r/faq/how-do-i-analyze-survey-data-with-a-simple-random-sample-design/
http://www.interactivecultures.org/2016/09/encoding-visualising-survey-data-using-r/
