---
title: "Classes & Services Data"
output: html_document
---

```{r loadPackages, warning=FALSE, message=FALSE}
#Remove when mergedinto main document as an appendix
if(!require(easypackages)){install.packages("easypackages")}
library(easypackages)
packages("dplyr", "data.table", "xda","ggplot2", "forcats", "readr", prompt = FALSE)
```

### Get Classes & Services Data

```{r loadClassesServices, message=FALSE, warning=FALSE}
#Get Data
Classes_Services <- read_csv("C:/Users/cweaver/Downloads/Classes_Services.csv", 
                   col_types = cols(AvailablePIF = col_integer(), 
                      ByPerson = col_integer(), CanSeeInstructor = col_integer(), 
                      CancellationHrs = col_integer(), 
                      ClassMins = col_integer(), CustSelfBook = col_integer(), 
                      Disabled = col_integer(), EmailReminders = col_integer(), 
                      HalfHour = col_integer(), MultipleInstructors = col_integer(), 
                      MustHaveCredit = col_integer(), MustPreBook = col_integer(), 
                      NumPerClass = col_integer(), OnTheHour = col_integer(), 
                      QuarterPast = col_integer(), QuarterTill = col_integer(), 
                      RescheduleDeadline = col_integer(), 
                      RuleCustomers = col_integer(), RuleFrontDesk = col_integer(), 
                      SMSReminders = col_integer(), ServicesId = col_integer(), 
                      ShowPublic = col_integer(), StandardPrice = col_integer()), 
                   na = "NA")

myData <- Classes_Services
rm(Classes_Services)
```

`ClassesServices.csv` returned `r dim(myData[1])` records with `r dim(myData[2])` variables.  Of the `r dim(myData)[2]` variables, `r nrow(myData %>% select_if(is.character))` is a `character` type and `r nrow(myData %>% select_if(is.numeric))` are `numeric`.

```{r}
glimpse(myData)
```

### Remove NA

Just as we experienced before, must remove the `NAs` with 0:

```{r}
myData <- myData %>%  mutate_if(is.integer, funs(replace(., is.na(.), 0)))
myData <- myData %>%  mutate_if(is.double, as.integer)
glimpse(myData)
```

That looks much better!

### Character to Factors

Change the variable `Type` from a character to a factor.
```{r}
myData <- myData %>% mutate_if(is.character, as.factor)
class(myData$Type)
```

### Explore Factors

```{r}
charSummary(myData)
```

```{r}
myData_factor <- myData %>% select_if(is.factor)
#myData_num <- myData %>% select_if(is.numeric)

for(i in 1:length(myData_factor)){
  print(names(myData_factor[i]))
  print(table(myData_factor[i]))
}

for(i in 1:length(myData_factor)){
  print(ggplot(myData_factor, aes_string(names(myData_factor[i]))) + geom_bar())
}
```

**I am uncertain how to define Class and Service - check with ClubReady**

### Evaluate Numerical Data

```{r}
myNumSum <- numSummary(myData)[, c(1,7,8,16,17)]
myNumSum <- tibble::rownames_to_column(myNumSum)
names(myNumSum)[5] <- "missPCT"
names(myNumSum)[1] <- "Variable_Name"
myNumSum <- arrange(myNumSum, desc(missPCT))
head(myNumSum, 20)
```

Good, no missing data!

#### Evaluate Variable Variances

```{r}
myVariance <- as.data.frame(apply(myData[,-c(1)], 2, var))
myVariance <- tibble::rownames_to_column(myVariance)
names(myVariance)[2] <- "Variance"
myVariance <-  myVariance %>% mutate(Variance2 = ifelse(Variance == 0, "No", "Yes"))
table(myVariance$Variance2)
```
All the variables have a variance > 0.

```{r}
if(table(myVariance$Variance2)[1] > 0){
  filter(myVariance, Variance2 == "No")
  VarNames <- myVariance %>% filter(Variance > 0) %>% select(rowname)
  myData <- myData %>% select(StoreId, unlist(VarNames))
}
```

### Duplicate Records
cat("The number of duplicated rows is", nrow(myData) - nrow(unique(myData)))

```{r showDupes}
myData[duplicated(myData),]
```

> Ask ClubReady if these should be removed

```{r eval=FALSE}
if(nrow(myData) - nrow(unique(myData)) > 0){
  head(myData[duplicated(myData),])
  myData <- myData[!duplicated(myData),]
}
```

### Final Output (Initial Data Cleaning)
glimpse(myData)


