---
title: "User Data"
output:
  prettydoc::html_pretty:
    theme: architect
    highlight: github
---

```{r echo=FALSE, message=FALSE, warning=FALSE}
if(!require(easypackages)){install.packages("easypackages")}
library(easypackages)
packages("plyr", "dplyr", "ggplot2", "readr", "funModeling", prompt = FALSE)
```

# Introduction

This document is provided in response to a request during a Valorem - ClubReady/Club Essentials Meeting March 20, 2018 2PM CT.

Below is a brief introduction to the User data provided to Valorem to develop a User Churn Model.  Unfortunately, the data does not provide sufficient information value to devlop a reasonable algorithmic predictive model.

# Get Data

```{r loadData, message=FALSE, warning=FALSE, echo=FALSE}
Users <- read_csv("C:/Users/cweaver/Downloads/Users.csv", progress = FALSE)
dim(Users)
print("There are 1.75 M records and 48 features in the User Data.")
Users <- sample_n(Users, 5000)
```

# Review Data

```{r}
glimpse(Users)
```

```{r fig.height = 10, fig.width=9}
plot_num(select(Users, -UserId))
```

```{r}
freq(Users, input = c("Gender", "UserType"))
```

